What can the Issues of GitHub and Googlecode tell us about Exception Fragilities in Android?

### 2014-09-03 android-stacks.tex
all over

\title{ What can GitHub and Googlecode Issues tell us about Exceptions in Android and Java? }

@@

\begin{abstract}

This paper reports a repository mining study which analyzed all the issues created on
Android projects available in GitHub (482 applications) and Google code (157 applications)
Overall, our research set includes 32,582 issues in GitHub and 41,674 issues in Googlecode 
from which 6,005 exception stack traces were extracted. Such stack traces were distilled and analyzed in 
combination with source code and bytecode analysis. This study 
consistently identifies common characteristics of reported 
exception stacks traces - e.g., the NullPointerException was the reported cause 
on 30,08\% of all analyzed exception stack traces, and was mentioned in approximately 
50\% of all projects analyzed. Moreover,  the cross-project analysis 
of exception stack traces enabled to consistently reveal   
fragilities of the exception-related code: 
(1) undocumented runtime exceptions signaled by third party code,
(2) undocumented checked exceptions thrown by Android native code
(3) unexpected exception wrappings (e.g., Errors being wrapped in checked exceptions) 
revealing that Java hybrid exception model is not fully used according to its purpose.
Such fragilities impose challenges to application robustness not only 
in Android environment but also to other systems based on Java exception model.

@@

@@

Along the recent years, we have witnessed an astonishing increase in the number 
mobile applications being developed and some of them becoming largely used. 
Such increase is motivated by pervasiveness of the World Wide Web 
and the unprecedented increase of global smartphone shipments -
the mobile industry shipped over 315 million smartphones in the last quarter of 2013 ~\cite{googleio}.

@@

In this context, Android has become a leading platform for such applications - thanks to its open-source 
model and hardware partners like Samsung, HTC, Motorola, Asus (besides Nexus Google's
 own device) ~\cite{gartner}.  Google estimates that there is over 1 billion Android active users per month ~\cite{googleio},
and the number of apps built on top of Android increases in a daily rate.

@@

In the same rate the number of a users increase, also increases 
the number of users affected by application faults and crashes.
If on the one hand such applications extend phones capabilities 
far beyond of the basic calls and textual messages, on the other hand
they have to face threats to application robustness ~\cite{was2010}.
Such applications have to cope with an increasing number of abnormal
computation states, arising from:
 noisy user inputs; faults in underlying middleware or hardware; 
faults on third party services and libraries; compatibility issues [ref]; 
connection with devices e.g., as GPS, camera; memory and battery restrictions; 
 programming errors, among others.

%Hence, in the same rate the number of mobile users increase, also increases 
%the number of users affected by such threats.

%faulty apps and app crashes.

@@

To do so we perform a post mortem analysis of the exception stack traces embedded on all issues
created on Android projects available in GitHub and Googlecode. Using a custom tool called ExceptionMiner,
 which we develop specifically for this study, we mine stack traces from issues across all Android projects on
GitHub and Googlecode. Overall, we analyzed all issues extracted from on 482 Android projects defined in
GitHub and 157 projects defined in Googlecode. Overall it corresponds to 74,256 issues (32,582 issues from GitHub projects 
and 41,674 issues from Googlecode projects) from which  6,005 stack traces were extracted and used as
 a source of information for our analysis. The stack trace analysis was augmented by additional information
extracted from JDK, Android Plaform and the applications using byte code and source code analysis.
 Manual inspection was used to leverage the understanding of exception stack traces and support further discussions and insights.

@@

\begin{figure} \centering \includegraphics[scale=0.8]{stacktrace.png}
\caption{Example of an Exception stack trace in Java.}
\label{fig:wrapping}
\end{figure}

>>>>

\title{What can the Issues of GitHub and Googlecode tell us about Exception Fragilities in Android? }

@@

%GitHub 315,92
% Googlecode: 127,456
%All: 159,048

\begin{abstract}
The number of mobile apps is increasing in a daily rate. If on the one hand they
extend phones capabilities far beyond of the basic calls, on the other hand they have to 
cope with an increasing number of exceptinal conditions 
(e.g., faults in underlying middleware or hardware; memory and battery restrictions). 
Therefore, mechanisms for exception detection and handling are not an optional add-on but a 
fundamental part of such apps. However, studies have shown that such mechanisms are the less 
understood and tested parts of the system. As a consequence they may affect the system the 
other way around, making the system even less robust.
This paper reports a study which mined the stack traces embedded on 
159,048 issues reported on Android projects hosted in GitHub (482 projs.) 
and Googlecode (157 projs.). The goal of this study was to: identify common characteristics 
of such traces and investigate the fragilities on the exception-related code that can be revealed
from them. Overall 6,005 exception stack traces were extracted, and analyzed in 
combination with source code and bytecode analysis. 
Some fragilities consistently detected in this study include: 
(1) undocumented runtime exceptions thrown by third party code;
(2) undocumented checked exceptions thrown by Android native code;
(3) unexpected exception wrappings (e.g., Errors being wrapped in checked exceptions),
revealing that Java hybrid exception model is not fully used according to its purpose.
Moreover, about 50\% of all analyzed projects reported at least one NullPointerExeption
as the root cause of an exception stack trace.
This study provide important insights on how such fragilities impose challenges 
to application robustness not only in Android environment but also to other 
systems based on Java exception model.

@@

%GitHub 31,592
% Googlecode: 127,456
%All: 159,048

@@

Along the recent years, we have witnessed an astonishing increase in the number 
mobile applications. Such increase is motivated by pervasiveness of the World Wide Web 
and the unprecedented increase of global smartphone shipments -
the mobile industry shipped over 315 million smartphones in the last quarter of 2013 ~\cite{googleio}.

@@

In this context, Android has become a leading platform - thanks to its open-source 
model and hardware partners like Samsung, HTC, Motorola, Asus (besides Nexus Google's
 own device) ~\cite{gartner}.  Google estimates that there is over 1 billion Android active users per month ~\cite{googleio},
and the number of apps built on top of Android increases in a daily rate.

@@

%In the same rate the number of a users increase, also increases 
%the number of users affected by application faults and crashes.

If on the one hand such applications extend phones capabilities 
far beyond of the basic calls and textual messages, on the other hand
they have to face an increasing number of threats to application robustness
 arising from: faults in underlying middleware and hardware, 
faults on third party services and libraries; compatibility issues; 
faults on connected devices (e.g. camera, GPS); memory and 
battery restrictions; among others.

%Hence, in the same rate the number of mobile users increase, also increases 
%the number of users affected by such threats.
%faulty apps and app crashes.

@@

To do so we perform a post mortem analysis of the exception stack traces embedded on all issues
created on Android projects available in GitHub and Googlecode. Using a custom tool called ExceptionMiner,
 which we develop specifically for this study, we mine stack traces from issues across all Android projects on
GitHub and Googlecode. Overall, we analyzed all issues extracted from on 482 Android projects defined in

%GitHub 31,592
% Googlecode: 127,456
%All: 159,048

GitHub and 157 projects defined in Googlecode. Overall it corresponds to 159,048 issues (31,592 issues from GitHub projects 
and 127,456 issues from Googlecode projects) from which  6,005 stack traces were extracted and used as
 a source of information for our analysis. The stack trace analysis was augmented by additional information
extracted from JDK, Android Plaform and the applications using byte code and source code analysis.
 Manual inspection was used to leverage the understanding of exception stack traces and support further discussions and insights.

@@

\begin{figure} \centering \includegraphics[scale=0.6]{stacktrace_bw.png}
\caption{Example of an exception stack trace in Java.}
\label{fig:wrapping}
\end{figure}
